Evaluation of the repository

### 2024-11-20 pages/badges.qmd
chore(badges): minor tweaks

| Criteria | ACM Results Reproduced | NISO ROR-R | IEEE Code Reproducible | Psychological Science Computational Reproducibility |
| - | - | - | - | - |
| Reproduced results (assuming (a) acceptably similar (b) reasonabe time frame (c) only minor troubleshooting) | ✅ | ✅ | ✅ | ✅ |
| README file with step-by-step instructions to run analysis | ❌ | ❌ | ❌ | ✅ |
| Dependencies (e.g. package versions) stated | ❌ | ❌ | ❌ | ✅ |
| Clear how output of analysis corrsponds to article | ❌ | ❌ | ❌ | ✅ |
: {tbl-colwidths="[50, 12.5, 12.5, 12.5, 12.5]"}

@@

> "All manuscripts submitted to Psychological Science are expected to be computationally reproducible. That is, a reader should be able to **run the authors’ analysis scripts on the authors’ data and reproduce the results reported in the manuscript, tables, and figures**. As part of the STAR review after conditional acceptance, we will conduct computational reproducibility checks.
>
> To ensure their work is computationally reproducible, authors should accompany analysis scripts with a **README file that provides clear step-by-step instructions** for repeating the analyses. Any **software dependencies (e.g., package versions) should be identified**. Authors should make **clear how the output of the analysis scripts corresponds to the results reported in the manuscript**. We strongly encourage authors to perform a reproducibility check within their own team before submitting a manuscript, as this will reduce delays at the conditional acceptance stage."
>
> @association_for_psychological_science_aps_psychological_2023
>
> "The Computational Reproducibility Badge will be awarded when authors take the necessary steps to ensure that reported results can be independently reproduced, **within a reasonable time frame**, by the STAR team. This is a standard that we expect from all articles submitted to Psychological Science; however, we appreciate that the community may currently lack the resources and skills required to write reproducible manuscripts. With that in mind, we are identifying and collating resources (see Educational Resources section) to help the community build the capacity to meet this standard. Eventually, we plan to make verified computational reproducibility a blanket requirement for all empirical articles."
>
> @hardwicke_transparency_2024

>>>>

| Criteria | ACM Results Reproduced | NISO ROR-R | IEEE Code Reproducible | Psychological Science Computational Reproducibility |
| - | - | - | - | - |
| Reproduced results (assuming (a) acceptably similar (b) reasonabe time frame (c) only minor troubleshooting) | ✅ | ✅ | ✅ | ✅ |
| README file with step-by-step instructions to run analysis | ❌ | ❌ | ❌ | ✅ |
| Dependencies (e.g. package versions) stated | ❌ | ❌ | ❌ | ✅ |
| Clear how output of analysis corresponds to article | ❌ | ❌ | ❌ | ✅ |
: {tbl-colwidths="[50, 12.5, 12.5, 12.5, 12.5]"}

@@

> "All manuscripts submitted to Psychological Science are expected to be computationally reproducible. That is, a reader should be able to **run the authors’ analysis scripts on the authors’ data and reproduce the results reported in the manuscript, tables, and figures**. As part of the STAR review after conditional acceptance, we will conduct computational reproducibility checks.
>
> To ensure their work is computationally reproducible, authors should accompany analysis scripts with a **README file that provides clear step-by-step instructions** for repeating the analyses. Any **software dependencies (e.g., package versions) should be identified**. Authors should make **clear how the output of the analysis scripts corresponds to the results reported in the manuscript**. We strongly encourage authors to perform a reproducibility check within their own team before submitting a manuscript, as this will reduce delays at the conditional acceptance stage."
>
> @association_for_psychological_science_aps_psychological_2024
>
> "The Computational Reproducibility Badge will be awarded when authors take the necessary steps to ensure that reported results can be independently reproduced, **within a reasonable time frame**, by the STAR team. This is a standard that we expect from all articles submitted to Psychological Science; however, we appreciate that the community may currently lack the resources and skills required to write reproducible manuscripts. With that in mind, we are identifying and collating resources (see Educational Resources section) to help the community build the capacity to meet this standard. Eventually, we plan to make verified computational reproducibility a blanket requirement for all empirical articles."
>
> @hardwicke_transparency_2024

### 2024-11-20 pages/protocol.qmd
docs(protocol): changes language from deviations to modifications
chore(badges): minor tweaks

* The publication was evaluated against reporting guidelines for DES:
    * @monks_strengthening_2019 - STRESS-DES: Strengthening The Reporting of Empirical Simulation Studies (Discrete-Event Simulation) (Version 1.0).
    * @zhang_reporting_2020 - The generic reporting checklist for healthcare-related discrete event simulation studies derived from the the International Society for Pharmacoeconomics and Outcomes Research Society for Medical Decision Making (ISPOR-SDM) Modeling Good Research Practices Task Force reports.
* The model code and associated artefacts (e.g. the GitHub repository shared by the authors) was evaluated against:
    * The criteria of badges related to reproducibility from various organisations and journals - namely:
        * National Information Standards Organisation (NISO)(@niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021)
        * Association for Computing Machinery (ACM) (@association_for_computing_machinery_acm_artifact_2020)
        * Center for Open Science (COS) (@blohowiak_badges_2023)
        * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)
        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)
    * Recommendations from the pilot STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
* This is timed

@@

## Major deviations from the protocol

There was one major deviation from the protocol...

@@

## Minor deviations from the protocol

There were some minor deviations from the protocol, which are explained below...

>>>>

* The publication was evaluated against reporting guidelines for DES:
    * @monks_strengthening_2019 - STRESS-DES: Strengthening The Reporting of Empirical Simulation Studies (Discrete-Event Simulation) (Version 1.0).
    * @zhang_reporting_2020 - The generic reporting checklist for healthcare-related discrete event simulation studies derived from the the International Society for Pharmacoeconomics and Outcomes Research Society for Medical Decision Making (ISPOR-SDM) Modeling Good Research Practices Task Force reports.
* The model code and associated artefacts (e.g. the GitHub repository shared by the authors) was evaluated against:
    * The criteria of badges related to reproducibility from various organisations and journals - namely:
        * National Information Standards Organisation (NISO)(@niso_reproducibility_badging_and_definitions_working_group_reproducibility_2021)
        * Association for Computing Machinery (ACM) (@association_for_computing_machinery_acm_artifact_2020)
        * Center for Open Science (COS) (@blohowiak_badges_2023)
        * Institute of Electrical and Electronics Engineers (IEEE) (@institute_of_electrical_and_electronics_engineers_ieee_about_2024)
        * Psychological Science (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2024)
    * Recommendations from the pilot STARS framework for the sharing of code and associated materials from discrete-event simulation models (@monks_towards_2024).
* This is timed

@@

## Modifications from the protocol

There was one major change from the protocol...

@@

There were also some minor changes, which are explained below...

### 2024-11-20 pages/repo_evaluation.qmd
chore(references): update hardwicke year
chore(badges): minor tweaks

**Institute of Electrical and Electronics Engineers (IEEE)** (@institute_of_electrical_and_electronics_engineers_ieee_about_nodate)

@@

**Psychological Science** (@hardwicke_transparency_2023 and @association_for_psychological_science_aps_psychological_2023)

>>>>

**Institute of Electrical and Electronics Engineers (IEEE)** (@institute_of_electrical_and_electronics_engineers_ieee_about_2024)

@@

**Psychological Science** (@hardwicke_transparency_2024 and @association_for_psychological_science_aps_psychological_2024)
